Revisiting the hydrodynamic modulation of short surface waves by longer waves

### 2024-10-16 paper.tex
Style fix
Fix typo

Solving analytically for the wavenumber requires dropping the spatial derivatives
of $k$ in Eq. \ref{eq:wavenumber} and assuming homogeneous $g$:

@@

Although in this paper we only explored the solutions for $k_L = 1$ and $k=10$
the results are not sensitive to different values of $k_L$, provided that the
amplitude $a_L$ is set such that the long-wave steepness $\varepsilon_L = a_L / k_L$
is the same.
Numerical simulations with $k/k_L = 10$ and $k/k_L = 100$ show little
sensitivity to the ratio $k/k_L$ (not shown), consistent with the results of
\citet{longuet1987propagation}.
Specifically, the short-wave steepness modulation is 1\% larger at
$\varepsilon_L = 0.27$ for $k/k_L = 10$ compared to $k/k_L = 100$, and 4\%
larger at $\varepsilon_L = 0.4$.
This suggests that as long as $k/k_L \gg 1$, the modulation amplitude is
largely independent of the ratio $k/k_L$.
These results can be reproduced with the companion numerical model.
Also not considered here are the short-wave trains that are oblique to the
longer waves, which is relatively straightforward to include
\citep{peureux2021unsteady}.

>>>>

Solving analytically for the wavenumber requires dropping the spatial derivatives
of $k$ in (\ref{eq:wavenumber}) and assuming homogeneous $g$:

@@

Although in this paper we only explored the solutions for $k_L = 1$ and $k=10$
the results are not sensitive to different values of $k_L$, provided the same
long-wave steepness $\varepsilon_L = a_L k_L$.
Numerical simulations with $k/k_L = 10$ and $k/k_L = 100$ show little
sensitivity to the ratio $k/k_L$ (not shown), consistent with the results of
\citet{longuet1987propagation}.
Specifically, the short-wave steepness modulation is 1\% larger at
$\varepsilon_L = 0.27$ for $k/k_L = 10$ compared to $k/k_L = 100$, and 4\%
larger at $\varepsilon_L = 0.4$.
This suggests that as long as $k/k_L \gg 1$, the modulation amplitude is
largely independent of the ratio $k/k_L$.
These results can be reproduced with the companion numerical model.
Also not considered here are the short-wave trains that are oblique to the
longer waves, which is relatively straightforward to include
\citep{peureux2021unsteady}.
